---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# haidagwaii

## Introduction

`haidagwaii` is an R data package that provides a spatial polygon object of the archipelago of Haida Gwaii, British Columbia called `haida_gwaii`. 

The projection is in Latitude and Longitude for the WGS84 geodetic datum.

## Usage

```{r}
# load required packages
library(haidagwaii)
library(broom)
library(ggplot2)

# project as BC Albers
haida_gwaii <- spTransform(haidagwaii::haida_gwaii, CRS("+init=epsg:3005"))

# convert into data frame
haida_gwaii <- broom::tidy(haida_gwaii)

# map
ggplot() +
geom_polygon(data = haida_gwaii, aes(x = long / 1000, y = lat / 1000, group = group),
               fill = alpha("black", 1/2)) +
  coord_equal() +
  scale_x_continuous("Easting (km)") +
  scale_y_continuous("Northing (km)")
```

## Installation

To install and load the development version from GitHub
```
install.packages("devtools") # if not already installed

library(devtools)
install_github("poissonconsulting/haidagwaii")
```

## License

The original data are available from <http://www12.statcan.gc.ca/census-recensement/2011/geo/bound-limit/files-fichiers/gcd_000b11a_e.zip>.
This does not constitute an endorsement by Statistics Canada of this product.
